\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{tipa}
\usepackage{phonetic}
\usepackage{pifont}
\usepackage{arydshln}
\usepackage{rotating}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage[applemac, utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage{enumerate}
\usepackage{textgreek}
\newcommand{\hand}{\ding{43}}
\usepackage{gb4e}
\usepackage{qtree}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{soul}
\usepackage{tikz-qtree-compat}
\tikzset{every tree node/.style={align=center, anchor=north}}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,automata}
\usepackage{natbib}
\bibliographystyle{apa}
\title{Phonetics Final Paper}
\author{Lisa Hofmann and Andrew Hedding}
\begin{document}
\maketitle
\section{Introduction}
\begin{itemize}
	\item Sande and Hedding hypothesize that there is phonological evidence that geminates contribute weight to syllables in Amharic and singleton codas do not.
	\item They argue that syllables closed by a geminate are heavy and that the Weight-to-Stress principle is high ranked in the language, causing stress to shift to syllables with geminates. 
	\item They mostly judge stress impressionistically, with minimal phonetic evidence. 
	\item The aim of this paper is to test their hypothesis by using phonetic analysis to determine if their predictions are borne out.
	\item We will also test another claim that they make: reduplication of geminates results in a singleton copy.	
\end{itemize}
\section{Geminates}
\begin{itemize}
\item Can we prove that geminates are distinct from singletons?
\item Each token is predicted to have a geminate and an identical singleton. Measure the duration of each to demonstrate that geminates are longer. 	
\end{itemize}

\section{Phonetic Correlates of Stress}
\subsection{Duration}
\begin{itemize}
\item I wonder how we should measure this. Most theories view geminates as both codas and onsets. Should we include half of the geminate? The whole thing? 
\item It might be circular to say that geminates cause stress and stress is determined by duration if geminates are by definition longer than singletons. 
\item If nothing else, we can discuss the issues with this in the final section. 	
\end{itemize}

\subsection{F0}
\begin{itemize}
\item Seems pretty straightforward. We should just standardize the range that we use and run all the sound clips through Praat. 
\end{itemize}

\subsection{Intensity}
\begin{itemize}
\item Same as above.
\end{itemize}

\section{Discussion}

\section{Conclusion}

%I have no idea why the bibliography won't work. Do you have any ideas? \bibliography{phonetics_bib}
\end{document}
